paper_code_documentation

### 2020-10-11 outputs/documents/notes/paper_code_documentation.Rmd
paper code implementation documentation

2. The following script was provided to download training dataset and create training examples:

@@

The above code was saved as a sh script and execute by the following command in the terminal:

``` {python, eval = FALSE}
./script.sh
```

And the above execution raised an error:

``` {python, eval = FALSE}
~/desktop/repos/ilm/data ~/desktop/repos/ilm
~/desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts ~/desktop/repos/ilm/data ~/desktop/repos/ilm
./get_arxiv_cs_abstracts.sh: line 5: wget: command not found
sed: illegal option -- r
usage: sed script [-Ealn] [-i extension] [file ...]
       sed [-Ealn] [-i extension] [-e script] ... [-f script_file] ... [file ...]
./get_arxiv_cs_abstracts.sh: line 5: wget: command not found
gunzip: can't stat: arxiv_cs_abstracts.txt.gz (arxiv_cs_abstracts.txt.gz.gz): No such file or directory
./get_arxiv_cs_abstracts.sh: line 7: sha256sum: command not found
~/desktop/repos/ilm/data ~/desktop/repos/ilm
~/desktop/repos/ilm
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
(project_ilm) (base) Kelis-MacBook-Pro:ilm kelichiu$ ./script.sh
~/desktop/repos/ilm/data ~/desktop/repos/ilm
./script.sh: line 4: data/get_arxiv_cs_abstracts.sh: No such file or directory
~/desktop/repos/ilm
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
(project_ilm) (base) Kelis-MacBook-Pro:ilm kelichiu$ ./script.sh
~/desktop/repos/ilm/data ~/desktop/repos/ilm
./script.sh: line 4: data/get_arxiv_cs_abstracts.sh: No such file or directory
~/desktop/repos/ilm
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'

```

>>>>

2. The following script was provided to download training dataset and create training example. It requires us saving the script as an sh file in order to execute it. I saved it in the repo root directory as script.sh.

@@

3. Execute the script by `./script.sh`. If permission error is displayed, try  `chmod +x script.sh` then execute the script again:

``` {sh, eval = FALSE}
# chmod +x script.sh
./script.sh
```

3.1. If the above execution raises an error that tells you that `arxiv_cs_abstracts.txt` is not found, go to this link to download the missing file: https://docs.google.com/uc?export=download&id=1N3MbvpgZAmNgiZgnpXAQFzHrU7Tt3Blb

3.2. Unzip the file and rename it to `arxiv_cs_abstracts.txt`, move it to `repo/data/raw_data/arxiv_cs_abstracts/`

4. The following script was provided to train the model (fine-tune GPT-2) by the training examples. It requires us saving the script as an sh file in order to execute it. I saved it in the repo root directory as training.sh. Execute it by `./training.sh`:

``` {sh, eval = FALSE}
DATASET=arxiv_cs_abstracts
TRAIN_DIR=train
EXAMPLES_DIR=data/char_masks/${DATASET}
python train_ilm.py \
	experiment_${DATASET} \
	${TRAIN_DIR} \
	${EXAMPLES_DIR} \
	--seed 0 \
	--train_examples_tag train \
	--eval_examples_tag valid \
	--eval_max_num_examples 512
```

The fine-tuning will start. According to the paper, it will take 1 day to complete with GPU. For a computer that doesn't have a GPU, it will take longer.
